Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-03 article.tex
bookmark

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}a):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics{images/mcgrid.pdf}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}[left], rendered using MC.}
  \label{fig:mcgrid}
\end{figure}

@@

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].
Figure~\ref{fig:cross_sections} plots the intensity profile in two lateral
cross sections of the viewed field, extracted from the images in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).
These plots demonstrate consistency in these cases, for most pixels.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross sections along the $X$-axis [a] and $Y$-axis [b] of
    and images rendered by either single-scattering and MC. The corresponding
    images appear in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).}
  \label{fig:cross_sections}
\end{figure}

\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a). Similarly, contributing photons that had experienced exactly  two or three scattering events yield respectively \cref{fig:scatter_order}(b) and
\cref{fig:scatter_order}(c). Clearly, first-order scatter is responsible
for most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long and dense part of the atmosphere, while a vertical LOS cuts short through the dense, lower part. Hence,
towards the horizon the probability of high order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first  order, (b) second order and (c) third scattering order.}
  \label{fig:scatter_order}
\end{figure}

@@

\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[htbp]
  \centering
  \begin{tabular}{cccccg}
    \toprule
    Haze Scene & Forward Model& Density & Isotropic PF & Absorbing & $\epsilon$ \\
    \midrule
    Front & Single & Low & & & 0.18 \\
     & MC & Low & & & 0.65 \\
    \cmidrule(r){1-5}
    Blobs & Single & Low & & & 0.14 \\
     & MC & Low & & & 0.65 \\
     & MC & Low & $\surd$  & & 0.49 \\
     & MC & Low & & $\surd$ & 0.83 \\
     & MC & High & & & 0.98 \\
    \bottomrule
  \end{tabular}
  \caption{Local error for the various simulations}
  \label{tbl:mass}
\end{table}

>>>>

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}a):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics{images/mcgrid.pdf}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}(a), rendered using MC.}
  \label{fig:mcgrid}
\end{figure}

@@

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
Figure~\ref{fig:cross_sections} plots the intensity profile in two lateral
cross sections of the viewed field, extracted from the images in
\cref{fig:simulation-results1}(d) and the corresponding MC derived photograph.
These plots demonstrate consistency in these cases, for most pixels.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering and MC forward models. 
    (a) cross sections of low density simulations (\cref{fig:simulation-results1}(d)
    and \cref{fig:simulation_particles}(a)). (b) cross sections of
    high density simulations (\cref{fig:simulation_particles}(d)).
  }
  \label{fig:cross_sections}
\end{figure}

\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a). Similarly, contributing photons that had experienced exactly  two or three scattering events yield respectively \cref{fig:scatter_order}(b) and
\cref{fig:scatter_order}(c). Clearly, first-order scatter is responsible
for most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long and dense part of the atmosphere, while a vertical LOS cuts short through the dense, lower part. Hence,
towards the horizon the probability of high order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}

@@

\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[htbp]
  \centering
  \begin{tabular}{cccccg}
    \toprule
    Haze Scene & Forward Model& Density & Isotropic PF & Absorbing & $\epsilon$ \\
    \midrule
    Front & Single & Low & & & 0.18 \\
     & MC & Low & & & 0.65 \\
    \cmidrule(r){1-5}
    Blobs & Single & Low & & & 0.14 \\
     & MC & Low & & & 0.65 \\
     & MC & Low & $\surd$  & & 0.49 \\
     & MC & Low & & $\surd$ & 0.83 \\
     & MC & High & & & 0.98 \\
    \bottomrule
  \end{tabular}
  \caption{Local error for the various reconstruction simulations}
  \label{tbl:mass}
\end{table}
